Prediction of the 2020 Presidential Election

### 2020-11-02 outputs/paper/paper.Rmd
gg

@@

# post-stratified estimates - number of trump votes
estimate_votes <- cell_counts %>% 
  mutate(predict_prop = proportion * estimate) %>% 
  group_by(total_num,state_name) %>% 
  summarise(predicted_vote = sum(predict_prop)) %>% 
  mutate(state_prediction = total_num*predicted_vote)

@@

cell_counts %>% arrange(num_records)

>>>>

cell_counts

@@

# post-stratified estimates - number of trump votes
estimate_votes <- cell_counts %>% 
  mutate(predict_prop = prop * estimate) %>% 
  group_by(state_name) %>% 
  summarise(predicted_vote = sum(predict_prop)) %>% ungroup()

@@
